\begin{thebibliography}{99}
 
    \bibitem[BB13]{BB13}
        Broňa Brejová,
        \emph{Skriptá k predmetu vyhľadávanie v texte},
        FMFI UK,
        2013.
        
    \bibitem[BV11]{BV11}
        Broňa Brejová a Tomáš Vinař,
        \emph{Metódy v bioinformatike},
        FMFI UK,
        2011.
        
    \bibitem[BW94]{BW94}
        Michael Burrows and David J Wheeler,
        \emph{A block-sorting lossless data compression algorithm},     
        Technical Report 124,
        1994.
        
    \bibitem[FM00]{FM00}
        Paolo Ferragina and Giovanni Manzini,
        \emph{Opportunistic data structures with applications},
        Proceedings of the 41st Annual Symposium on Foundations of Computer
        Science, strany 390-398,
        2000.
        
    \bibitem[PTW01]{PTW01}
        Pavel A. Pevzner, Haixu Tang and Michael S. Waterman,
        \emph{An Eulerian path approach to DNA fragment assembly},
        Proc Natl Acad Sci USA
        2001.
        
    \bibitem[MM90]{MM90}
        Udi Manber and Gene Myers,
        \emph{Suffix arrays: a new method for on-line string searches},
        First Annual ACM-SIAM Symposium on Discrete Algorithms, strany 319-327,
        1990.
        
    \bibitem[AKO04]{AKO04}
        Mohamed Ibrahim Abouelhodaa, Stefan Kurtzb and Enno Ohlebuscha,
        \emph{Replacing suffix trees with enhanced suffix arrays},
        Journal of Discrete Algorithms 2,
        2004.
        
    \bibitem[NZC09]{NZC09}
        Ge Nong, Sen Zhang and Wai Hong Chan,
        \emph{Linear Suffix Array Construction by Almost Pure Induced-Sorting},
        2009 Data Compression Conference, strany 193-202,
        2009.
        
    \bibitem[KS03]{KS03}
        Juha Kärkkäinen and Peter Sanders,
        \emph{Simple Linear Work Suffix Array Construction},
        Automata, Languages and Programming. Lecture Notes in Computer Science
        2719, strana 943,
        2003.
        
    \bibitem[GGV03]{GGV03}
        Roberto Grossi, Ankur Gupta and Jeffrey Scott Vitter,
        \emph{High-order entropy-compressed text indexes},
        Proceedings of the 14th Annual SIAM/ACM Symposium on Discrete Algorithms, strany 841-850,
        2003.
        
    \bibitem[JS12]{JS12}
        Jochen Singer,
        \emph{A Wavelet Tree Based FM-Index for Biological Sequences in SeqAn},
        Master thesis,
        Freie Universit\"{a}t Berlin,
        2012.
        
    \bibitem[NP11]{NP11}
        Nicolas Phillipe, Mika\"{e}l Salson, Thierry Lecroq, Martine Léonard, Thér\`{e}se Commes and Eric Rivals,
        \emph{Querying large read collections in main memory: a versatile data structure},
        BMC Bioinformatics 2011, 12:242,
        2011.
        
    \bibitem[SD11]{SD11}
        Jared T. Simpson and Richard Durbin
        \emph{Efficient de novo assembly of large genomes using compressed data structures},
        Genome Research 2012, 22: 549-556,
        2011.

\end{thebibliography}